### 2013-06-17 gapoly.Rmd
changed dataframe eg

Eg (for the values in the previous code snippet):

Consider polynomial $x_1^2 \times x_3 + x_3^3 + x_1 \times x_2$

One possible coding would be (the semicolons separate components, the commas seperate variables):

@@

@@

Let's create a dataframe for testing:

```{r, fig.width=12}
set.seed(101)
x1 <- seq(0, 8 * pi, length.out = 201)/pi
x2 <- sin(x1)^2
x3 <- abs(cos(x2))
y  <- x1*x2 - x1*x3 + x3^3 + rnorm(201,0,.15) # a latent variable with some noise
df <- data.frame(y=y,x1=x1,x2=x2,x3=x3) # make data frame
```

This binary coding is useful to use the binary GA rbga.bin() from package `genalg` (see below):

@@

  function(chromosome) {
    formula <- paste0("y ~ ", make.formula(chromosome, n.vars, max.compts))
    model <- lm(formula, data=df)
    return( sqrt(mean(residuals(model)^2)) ) #rbga.bim tries to minimize
  }
}

#############################
# Unleash the chromosomes of war!
GAmodel <- rbga.bin(size = max.degree*n.vars*max.compts, 
                    popSize = 100, 
                    iters = 100, 
                    mutationChance = 0.01, 
                    elitism = TRUE, 
                    evalFunc = evalFuncFactory(df, n.vars, max.compts))

>>>>

Eg: consider polynomial $x_1^2 \times x_3 + x_3^3 + x_1 \times x_2$

One possible coding -- for the values in the previous code snippet -- would be:

@@

(the semicolons separate components, the commas seperate variables)

@@

Let's create a dataframe for testing. Notice that the data frame columns name must be called $y$ for the output value, and $x_i$ for the input values:

```{r, fig.width=12}
set.seed(102)
x1 <- seq(0, 8 * pi, length.out = 201)/pi
x2 <- sin(x1)^2
x3 <- abs(cos(x1))
y  <- x1*x2 - x1*x3 + x3^3 + rnorm(201,0,.15) # a latent variable with some noise
df <- data.frame(y=y,x1=x1,x2=x2,x3=x3) # make data frame
```

This binary coding is useful to use the binary GA `rbga.bin()` from package `genalg` (see below):

@@

  function(chromosome) {
    formula <- paste0("y ~ ", make.formula(chromosome, n.vars, max.compts))
    model <- lm(formula, data=df)
    # rbga.bin() minimizes, so the rmse will be smaller as the interations advance
    return( sqrt(mean(residuals(model)^2)) ) 
  }
}

#################################
# Unleash the chromosomes of war!
#################################
GAmodel <- rbga.bin(size = max.degree*n.vars*max.compts, 
                    popSize = 150, 
                    iters = 100, 
                    mutationChance = 0.01, 
                    elitism = TRUE, 
                    evalFunc = evalFuncFactory(df, n.vars, max.compts))
